{\it Maxwell's Silver Hammer:}\\ On pulsed microwave acoustic resonant viral inactivation

### 2021-03-08 documents/brillouin_pulse_math.tex
Adding supplemental

Based on Yang's inactivation thresholds, for instance, at 9 GHz, assuming that a torso is about 10 penetration depths in radius and the hypothetical Brillouin train drives the virus equally effectively as, implementing a precursor would decrease the field required at the skin to a perfectly practicable 1 kV/m, rather than an air-ionizing 6.6 MV/m ($\frac{1}{\sqrt{10}}=0.316$ versus $e^{-10}=4.5e^{-5}$).

@@

\begin{figure}[H]
	%	\makebox[\textwidth][c]{
	\includesvg[width=\textwidth]{muscle_pulse_8cm_minimize_test2}
	\caption{}
\end{figure}

>>>>

Based on Yang's inactivation thresholds, for instance, at 9 GHz, assuming that a torso is about 10 penetration depths in radius and the hypothetical Brillouin train drives the virus equally effectively as a pure sine, implementing a precursor would decrease the field required at the skin to a perfectly practicable 1 kV/m, rather than an air-ionizing 6.6 MV/m ($\frac{1}{\sqrt{10}}=0.316$ versus $e^{-10}=4.5e^{-5}$).

@@

%\begin{figure}[H]
%	%	\makebox[\textwidth][c]{
%	\includesvg[width=\textwidth]{muscle_pulse_8cm_minimize_test2}
%	\caption{}
%\end{figure}

### 2021-03-08 documents/summary.tex
Adding supplemental

When phage is rapidly immersed in solution of high osmotic strength, the active system that maintains osmotic equilibrium is overwhelmed, and the resulting pressure ruptures the capsid when it exceeds about 100 atm \cite{Osmotic2003}. By $\sigma = pr / 2t $ t = 5.7 nm\cite{Head1988} and r=60 nm, capsid strength should be about 53 MPa, less than the 100 to 300 MPa cited by \cite{Bacteriophage2004}.
%((100 atm * 60 nanometers) / (2*(5.7 nanometers))) to MPa

@@

PMT dark counts and ambient light were removed by synchronous photon counting\cite{Measurement1966} - add when light is on, subtract when light is off.  This cannot be done with luminescence. Further filtering could be done by fluorescence lifetime discrimination.

@@

For the Eppenwolf, the lower bound is the lowest voltage measured on the diode detector through the sweep (at 12 GHz), (raw unconverted voltage across frequency can be seen at\ghfile{firmware/eppenwolf/runs/phage_experiment_12/screenshot_192.168.0.38_2020-11-26_13:38:24.png} - it is not recorded which detector this was seen at) multiplied by the FDTD results for the coplanar waveguide voltage to channel field scaling factor. The upper bound is the maximum voltage seen over the frequency sweep multiplied by the same FDTD factor.

@@

Funded in part by the author's company, SafeSump Inc., and Ideal Consulting Inc., and the author's parents. The author was at YorkU for the duration of this project.

>>>>

When phage is rapidly immersed in solution of differing osmotic strength, the active system that maintains osmotic equilibrium is overwhelmed, and the resulting pressure ruptures the capsid when it exceeds about 100 atm \cite{Osmotic2003}. By $\sigma = pr / 2t $ t = 5.7 nm\cite{Head1988} and r=60 nm, capsid strength should be about 53 MPa, less than the 100 to 300 MPa cited by \cite{Bacteriophage2004}.
%((100 atm * 60 nanometers) / (2*(5.7 nanometers))) to MPa

@@

PMT dark counts and ambient light were removed by synchronous photon counting\cite{Measurement1966} - add when light is on, subtract when light is off. The fluorescence excitation light was 50\% square-wave modulated at 100 khz.  This cannot be done with luminescence. Further filtering could be done by fluorescence lifetime discrimination.

@@

For the Eppenwolf, the lower bound is the lowest voltage measured on the diode detector through the sweep (at 12 GHz), (raw unconverted voltage across frequency can be seen at\ghfile{/firmware/eppenwolf/runs/phage_experiment_12/screenshot_192.168.0.38_2020-11-26_13:38:24.png} - it is not recorded which detector this was seen at) multiplied by the FDTD results for the coplanar waveguide voltage to channel field scaling factor. The upper bound is the maximum voltage seen over the frequency sweep multiplied by the same FDTD factor.

@@

Funded in part by the author's company, SafeSump Inc., and Ideal Consulting Ltd., and the author's parents. The author was at YorkU for the duration of this project.

### 2021-03-08 documents/supplemental.tex
Adding supplemental

\clearpage
\rule{\linewidth}{0.2pt}

There seems to be a discrepancy between \cite{Efficient2015} and our reading of [C95.1-2005].

They use a threshold in open public space of $100(f/3)^{1/5} \text{ W/m}^2$. The 115 W @ 6 GHz figure they provide corresponds to this equation with a coefficient of 100.

For Table 9, general public, the equation is $18.56 (f)^{0.699} \text{ W/m}^2$, or $64.93 \text{ W}/\text{m}^2$ @ 6 GHz.

Different versions of the IEEE standard have used equations of equivalent form but with different coefficients [Wu 2015]; it is entirely possible that we have retrieved the wrong standard.

\PRLsep{{\itshape Wherein an oscillator is designed }}

Many

Three incorrect pieces of information conspired to lead us to try to develop an inexpensive ultrawideband oscillator.

\begin{itemize}
	\item The assumption that a broadband frequency sweep would drastically improve the inactivation threshold, and moreover that 
	\item The ideal 
	\item The assumption that the only commercially available oscillators in this frequency range were expensive YIG-tuned devices.
\end{itemize}

>>>>

\clearpage
%\rule{\linewidth}{0.2pt}
%
%
%There seems to be a discrepancy between \cite{Efficient2015} and our reading of [C95.1-2005].
%
%They use a threshold in open public space of $100(f/3)^{1/5} \text{ W/m}^2$. The 115 W @ 6 GHz figure they provide corresponds to this equation with a coefficient of 100.
%
%For Table 9, general public, the equation is $18.56 (f)^{0.699} \text{ W/m}^2$, or $64.93 \text{ W}/\text{m}^2$ @ 6 GHz. 
%
%Different versions of the IEEE standard have used equations of equivalent form but with different coefficients [Wu 2015]; it is entirely possible that we have retrieved the wrong standard.
%
%\rule{\linewidth}{0.2pt}

\section{Wherein a wideband oscillator is designed}

Several incorrect pieces of information conspired to lead us to try to develop an inexpensive ultrawideband oscillator.

\begin{itemize}
	\item The
	\item The assumption that a broadband frequency sweep would drastically improve the inactivation threshold, and moreover that 
	\item The ideal 
	\item The assumption that the only commercially available oscillators in this frequency range were expensive YIG-tuned devices.
\end{itemize}

Besides the AD (formerly Hittite) HMC732 device, ADF5355 and lmx2615
